---
title: "Course Project: Shiny Application and Reproducible Pitch "
author: "Jack Mok"
date: "October 10, 2016"
output: ioslides_presentation
---

##Overview

This is part of deliverables for the course Developing Data Products as pat of the Coursera Data Science Specialization

The application is written by Shiny and plotly, and can be accessed by https://jackskmok.shinyapps.io/ShinyApplicationPitchProject

Source code for ui.R and server.R files can be accessed from Githup repo:
https://github.com/jackskmok/ShinyApplicationPitchProject.git

##Web Applciation functionality 
* This applicaiton is that provide a tool to explore the car performance in terms of Miles Per Gallon(MPG).
* Select the different Cylinders to explore the relationship between the Cylinders and MPG) with different distribution options.

* Providing the base regression analysis comparations using Displacement, Horse Power, Weight and all these three.
* By using the dropmenu options, user can select different predicter to analysis the regression of MPG.
* The diagnostics plot of Regression including Resdiuals vs Fitted, Normal QQ, Scale-Location, and Residuals vs Leverage.

##mtcars Dataset 
```{r warning = FALSE,echo=FALSE}
summary(mtcars)
```
##Plots 
```{r warning = FALSE,echo=TRUE, message=FALSE}
par(mfrow=c(2,3))
hist(mtcars$mpg, breaks = 5, col = 'blue', 
     border = 'white', xlab = "Miles/(US) gallon"); 
plot(lm(mpg ~ wt, data = mtcars))
```
